\chapter{Conclusion and Future Work} \label{chapter5}
This chapter outlines several lines of future work based on the outcomes of
this research.  The future work is then followed by the conclusions drawn from
this work and a discussion of their impact.

\section{Future Work}
Several lines of research following this work are presented in this section.
First and foremost, in order to put this technique into use on production
systems, the proof of concept \ac{W-SWFIT} application must be completed.
Furthermore, while automation was a consideration while conducting this
research, it was not implemented.  To be effective in a production environment,
the entire \ac{AFP} process must be automated.

One especially relevant and interesting line of effort that should follow this
work is to better identify when the underlying system has changed enough to
require retraining.  While the process is automated, it will unlikely be
necessary after every software update.  In order to avoid unnecessary use of
resources, this process could be explored.

As was demonstrated with the boosted decision trees, other statistical
classifiers could be explored.  The \ac{AFP} framework is not limited to a
single predictor~\cite{irrera2015}.  A series of prediction models can be used
to vote on the state of a system, the output being the majority.  In addition
to exploring other statistical learning models, additional states (or classes)
could be explored.  For example, instead of a failure state, a classification
model could be used to predict when a system would be idle to know when best to
install software updates.  Further, a classification model may be able to
automate the classification and prediction of when a target was under a
malicious attack in a method similar to the \ac{AFP} framework.

An additional area of exploration should be to better identify how fault
injection actually affects the underlying system.  This research has shown that
in some cases, it can be extremely difficult to identify areas that will create
realistic failure conditions with any preceding indicators.  Even when
constrained, a single library can have hundreds of injection points.
Furthermore, in some cases, even when all injection points are tested, none may
lead to a realistic failure.  For this reason, the additional fault loads play
an integral role.

The use of additional system statistics in conjunction with reported errors
could be explored but as Salfner, et al.~\cite{salfnerSurvey} point out, it is
difficult to distinguish between normal operations or increased work load using
this type of information.  In this work, the only possible outcomes of fault
injection were fail immediately, or no fail.  For this reasons, the use of this
data was not explored.

Finally, the integration of actual failure data with the \ac{AFP} framework
should be explored.  Bootstrapping could be used to better integrate actual
failure data into the training phase if it is observed. 

\section{Conclusion}
This research explored the use of the \ac{AFP} framework with additional fault
loads to predict failure using reported errors in the \ac{MS} \ac{DC}s.  It has
been shown that it is possible to predict failure in modern \ac{MS} enterprise
authentication architecture given a representative fault load.  Unfortunately,
at the time of writing, two out of the three fault loads introduced in this
research did not create failure conditions that could be predicted due to the
fact that there were no preceding indicators of failure.  This was a stated
limitation of the research.  However, the new fault loads are not useless.  As
was demonstrated with the \ac{SVM} predictor, the underlying system changes can
introduce or eliminate an applications vulnerability to certain types of
faults.  For this reason, if the \ac{AFP} framework is implemented on \ac{MS}
\ac{DC}s, all fault loads should be used in the execution and training phases.

Perhaps most interestingly, fault injection as was used in the original
\ac{AFP} framework implementation, had two outcomes: no failure occurred, or
failure occurred immediately.  In the controlled virtual environment, failure
was predictable using polled system health information, but perhaps the
indicators used to predict the failure were not actual errors but the fault
injection tool itself injecting faults.  Since during the golden runs, the
fault injection tool never wrote to another processes memory, it is possible
that a predictor trained using system health information would associate these
operations with failure.  Furthermore, even only using the Operator for Missing
Function Call (OMFC), there were still thousands of injection points in the
Windows Server 2008 operating system.  Identifying the handful that may
activate in a realistic way without crashing the target service immediately is
not trivial.  Clearly more work must be done to validate using fault injection
alone in the \ac{AFP} framework.

In addition to the new fault loads introduced in this work, a load generator
has also been presented:  \ac{D-PLG}, capable of sufficiently simulating peak
usage of a \ac{MS} enterprise \ac{DC}.  Additional uses for \ac{D-PLG} outside
of use in the \ac{AFP} framework include capacity planning/sizing, network
security testing and auditing, and software testing.  This research also
introduced \ac{W-SWFIT} which can be used to perform fault injection for a
variety of additional uses like software testing and auditing.

The impact of this research should not be over estimated.  As mentioned, a
major limitation of this technique is that it is not able to predict malicious
acts or \emph{Act of God} events.  Furthermore, the data generated are still
simulated data and as such, may not completely capture all possible failure
events.  The \ac{AFP} framework as presented here will however provide more
reliable predictions than are currently available today.

In conclusion, the modified \ac{AFP} framework as presented here can be used to
effectively predict failures that might occur in a production environment and
is capable of adapting to underlying system changes using only reported errors.
For these reasons, it is recommended that if the \ac{AFP} framework is to be
implemented as laid out in this research, all fault loads should be integrated
to maximize the frameworks ability to adapt to system changes.  To improve the
efficacy of a predictor trained using this generated data, real failure data
and additional predictors can easily be integrated if available.  Finally, real
failure data is difficult to obtain given how rare failure is in modern
systems.  Unfortunately, even after it is obtained, it can rapidly become
deprecated by underlying system changes.  Using the \ac{AFP} with the fault
loads introduced in this work to generate simulated failure data is the next
best thing to having real data and provides more useful predictions than are
available with no failure data.
