\date{September 2016}
\ReportDate{10--09--2016} \ReportType{Master's Thesis}
\DatesCovered{Sept 2015 --- Sep 2016}

\Title{\centering \MakeUppercase{Data Driven Device Failure}\\
                          \MakeUppercase{ Prediction}}

%\ContractNumber{DACA99--99--C--9999}

%\GrantNumber{}
%\ProgramElementNumber{}
%\ProjectNumber{09ENP???}
%\TaskNumber{}
%\WorkUnitNumber{}

\Author{Paul L. Jordan}

\PerformingOrg{Air Force Institute of Technology\\[-1pt]
    Graduate School of Engineering and Management (AFIT/EN)\\[-1pt]
    2950 Hobson Way\\[-1pt]
    WPAFB OH 45433-7765}

\POReportNumber{AFIT/GCS/ENG/17-M01}

\SponsoringAgency{National Information Assurance Education and Training\\[-1pt]
	Program\\[-1pt]
9800 Savage Road\\[-1pt]
Fort Meade, Maryland 20755-6744\\[-1pt]
410-854-6206\\[-1pt]
Email:  gmellis@nsa.gov; aeshaff@nsa.gov }

\Acronyms{NIETP}
%\SMReportNumber{}
\DistributionStatement{DISTRIBUTION STATEMENT A:\\[-1pt]
\MakeUppercase{Approved for Public Release; distribution unlimited.}}

\Abstract{As society becomes more dependent upon computer systems to perform
increasingly critical tasks, ensuring those systems do not fail becomes more
important. The Air Force, much like many other organizations, depends heavily
on desktop computers for day to day operations. Unfortunately, the software
that runs on these desktop computers is still written by humans and as such, is
still subject to human error and consequent failure. A natural solution is to
use statistical machine learning to predict failure. However, since failure is
still a relatively rare event, obtaining labelled training data to train these
models is not trivial. This work explores predicting failure in the Microsoft
enterprise authentication service using realistically generated failure data in
an effort to increase up-time in desktop computers and improve mission
effectiveness.}

\SubjectTerms{Thesis, Failure Prediction, Machine Learning}

\NumberPages{???}
%\ReportClassification{}
%\PageClassification{}
%\AbstractClassification{}
\AbstractLimitation{U}

\ResponsiblePerson{Dr. G. Peterson, AFIT/ENG}

\RPTelephone{(937) 255-????, x????; gilbert.peterson@afit.edu}

\MakeRptDocPage
